Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-23 05_calibration_data.Rmd

![Thinning by aggregation over a 30 second interval (down from 1 second) preserves track structure while reducing the data volume for computation. Here, thinned positions are shown as purple squares, with the size of the square indicating the number of positions within the 30 second bin used to obtain the average position. Green points show the median smoothed data from Figure 4, while the raw data are shown in grey.](figures/fig_calib_smooth_thin.png)

@@

![Classifying thinned data into residence patches yields robust estimates of the duration of known stops. The island of Griend (53.25$^{\circ}$N, 5.25$^{\circ}$E) is shown in beige. Residence patches (green polygons; function parameters in text) correspond well to the locations of known stops (purple crossed-squares). However, the algorithm identified all areas with prolonged residence, including those which were not intended stops (n = 12; green polygons without crossed-squares). The algorithm also failed to find two stops of 6 and 15 seconds duration, since these were lost in the data thinning step (crossed-square without green polygon shows one of these).](figures/fig_calib_residence.png)

>>>>

![Thinning by aggregation over a 30 second interval (down from 1 second) preserves track structure while reducing the data volume for computation. Here, thinned positions are shown as purple squares, with the size of the square indicating the number of positions within the 30 second bin used to obtain the average position. Green points show the median smoothed data from Figure 4, while the raw data are shown in grey. The area shown is the upper rectangle in Figure 3.](figures/fig_calib_smooth_thin.png)

@@

![Classifying thinned data into residence patches yields robust estimates of the duration of known stops. The island of Griend (53.25$^{\circ}$N, 5.25$^{\circ}$E) is shown in beige. Residence patches (green polygons; function parameters in text) correspond well to the locations of known stops (purple crossed-squares). However, the algorithm identified all areas with prolonged residence, including those which were not intended stops (n = 12; green polygons without crossed-squares). The algorithm also failed to find two stops of 6 and 15 seconds duration, since these were lost in the data thinning step (crossed-square without green polygon shows one of these). The area shown is the lower rectangle in Figure 3.](figures/fig_calib_residence.png)

### 2020-11-23 index.rmd

--- 
knit: "bookdown::render_book"
title: "Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data"
author:
    - Pratik R. Gupte
    - Christine E. Beardsworth
    - Orr Spiegel
    - Emmanuel Lourie
    - Allert Bijleveld
date: "`r Sys.Date()`"
output: bookdown::pdf_document2
documentclass: article
toc-depth: 2
secnumdepth: 2
geometry: "left=4cm, right=3cm, top=2.5cm, bottom=2.5cm"
bibliography: [references.bib]
link-citations: yes
github-repo: pratikunterwegs/atlas-best-practices
description: "Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data"
---

>>>>

--- 
knit: "bookdown::render_book"
title: "Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data"
author:
    - Pratik R. Gupte
    - Christine E. Beardsworth
    - Orr Spiegel
    - Emmanuel Lourie
    - Allert I. Bijleveld
date: "`r Sys.Date()`"
output: bookdown::pdf_document2
documentclass: scrartcl
toc-depth: 2
secnumdepth: 2
geometry: "left=4cm, right=3cm, top=2.5cm, bottom=2.5cm"
bibliography: [references.bib]
link-citations: yes
github-repo: pratikunterwegs/atlas-best-practices
description: "Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data"
---
